Different Interaction Rates

### 2022-12-05 graphs_newt_snakes/interaction_rate_inv.Rmd
I finished writing

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA1_lit_interrate_file
#cfile=GA1_cor_interrate_file 
 # pattern="1e-11_5_1e-11_5_0"
 # pattern="1e-11_5_1e-11_5_0"  
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)

  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(interrate)))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

@@

pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=GA1_lit_interrate_file
#cfile=GA1_cor_interrate_file 
 # pattern="1e-11_5_1e-11_5_0"
 # pattern="1e-11_5_1e-11_5_0"  
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)

  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_pop_size, group=interrate, color="Snake"),)+
    geom_line(aes(generation, Newt_pop_size, group=interrate, color="Newt"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake" = "steelblue", "Newt" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern),]) +
    geom_line(aes(generation, num_newts_By_num_snakes, col=factor(interrate)))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

@@

 my_plot <- ggplot(params, aes(newt,  paste0(interrate, "_", snake, "_", rep))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

@@

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
 file$generation<-as.numeric(file$generation)
 file$Snake_mean_Pheno<-as.numeric(file$Snake_mean_Pheno)
 file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, as.numeric(dif), group=interrate, col="dif"))+
    #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

@@

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake Phenotype")+
scale_fill_viridis_c(option = "plasma")
}

@@

newt$info <- "middle"
newt$info[newt$location %in% c(0, col_num-1, col_num*row_num-1-col_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(col_num-2)), seq(col_num, (col_num*row_num-col_num-2), col_num), seq((col_num-1+col_num), (col_num*row_num-1-col_num-col_num), col_num),  c((col_num*row_num-col_num):(col_num*row_num-2)))]   <- "edge"

@@

generations

```{r, graphing by gen}

>>>>

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern,interrate_cap){
#file=GA1_lit_interrate_file
#cfile=GA1_cor_interrate_file 
 # pattern="1e-11_5_1e-11_5_0"
 # pattern="1e-11_5_1e-11_5_0"  
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
  lp_trial = last_point[which(last_point$snake_newt_rep==pattern &last_point$interrate<=interrate_cap),]

  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +

    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
    geom_point(data=lp_trial, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(interrate)),size = 3)+

    geom_point(data=lp_trial, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(interrate)),size = 3)+ 
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
    geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, col=factor(interrate)))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

@@

pop_size_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern, interrate_cap){
#file=GA1_lit_interrate_file
#cfile=GA1_cor_interrate_file 
 # pattern="1e-11_5_1e-11_5_0"
 # pattern="1e-11_5_1e-11_5_0"  
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)

  last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
  lp_trial = last_point[which(last_point$snake_newt_rep==pattern &last_point$interrate<=interrate_cap),]

  plot_1 <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_pop_size, group=interrate, color="Snake"),)+
    geom_line(aes(generation, Newt_pop_size, group=interrate, color="Newt"))+

    geom_point(data=lp_trial, aes(generation, Snake_pop_size, color="Snake", shape=factor(interrate)),size = 3)+

    geom_point(data=lp_trial, aes(generation, Newt_pop_size, color="Newt", shape=factor(interrate)),size = 3)+ 
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake" = "steelblue", "Newt" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))
cor_plot <- ggplot(cfile[which(cfile$gen>=min_gen & cfile$gen<=max_gen & cfile$snake_newt_rep==pattern & file$interrate<=interrate_cap),]) +
    geom_line(aes(generation, num_newts_By_num_snakes, col=factor(interrate)))+
    #ggtitle(title, subtitle = subt) +
    ylim(-1.1, 1.1)+
    #xlab(x_label_cor) + ylab(y_label)+
    theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(),
                      plot.margin=unit(c(-0.5,1,1,1), "cm"))

@@

 my_plot <- ggplot(params, aes(newt, paste0(snake, "_", interrate))) +    # Create heatmap with ggplot2
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_tile(aes(fill = get(fill_line)))+theme(axis.text.x = element_text(angle = 45, hjust=1, size = 10), axis.text.y = element_text(size = 10))

@@

trends_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen, rep){
 file$generation<-as.numeric(file$generation)
 file$Snake_mean_Pheno<-as.numeric(file$Snake_mean_Pheno)
 file$Newt_mean_Pheno<-as.numeric(file$Newt_mean_Pheno)
 file$group_rate<- paste0(file$group, "_", file$interrate)

 last_point <- file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)

  plot <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    geom_line(aes(generation, as.numeric(dif), group=interrate, col="dif"))+
    #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=interrate, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=interrate, color="Newt_mean_Pheno"))+
    geom_point(data=last_point, aes(generation, Snake_mean_Pheno, color="Snake_mean_Pheno", shape=factor(interrate)))+ #, shape=cost, col="dif"
    geom_point(data=last_point, aes(generation, Newt_mean_Pheno, color="Newt_mean_Pheno", shape=factor(interrate)))+
    geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
       theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
  return(plot)
}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, rep, interrate_cap){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen & file$rep==rep & file$interrate<=interrate_cap),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen, rep ",rep)) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif, shape=factor(interrate)))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

@@

if(type != "num_ind"){
main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Toxicity/Resistance")+
 scale_fill_viridis_c()
}
if(type == "num_ind"){
main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
              subtitle = paste0(file_name, ", Generation: ", spegen),
              fill = "Newt/Snake PopSize")+
scale_fill_viridis_c(option = "plasma")
}

@@

newt$info <- "middle"

#need to look into, coloring problem
newt$info[newt$location %in% c(0, row_num-1, col_num*row_num-row_num, col_num*row_num-1)] <- "corner"

newt$info[newt$location %in% c(c(1:(row_num-2)), seq(row_num, (col_num*row_num-row_num-2), row_num), seq((row_num-1+row_num), (col_num*row_num-1-row_num), row_num),  c((col_num*row_num-row_num+1):(col_num*row_num-2)))]   <- "edge"

@@

## How Often do Newts and Snakes Interact {.tabset}
First, I wanted to do some data exploration! So I examined how manipulating the interaction rate would effect some population dynamics. I wanted to pin-point how often snakes could potentially and actuality interact with newts (one is looping through snakes with newts near by and one is counting the amount of times a snake encountered a newt, respectively). These are presented as histograms colored by the interaction rate (look closely at title). I also wanted to explore how interaction rate could impact the population size and mean phenotype of snakes and newts. These are also shown as histograms where color indicates the interaction rate. I also looked for an interaction between interaction rate, the population size of newts and snakes, and the number of interactions that occurred within a generation.

### Potential Interaction
```{r, how oftern do they interact Potential Interaction}
ggplot(GA1_lit_interrate_file)+
  ggtitle("Potential Interaction") +
  xlab("Snake can Potentially Find a Newt, Param: snake_found_newt") +
  ylab("Count") +
  geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black")) 
```

### True Number of Interactions
```{r, True Number of Interactions}
ggplot(GA1_lit_interrate_file)+
  ggtitle("Number of Interactions") +
  xlab("Snake found a Newt, Param: newt_found") +
  ylab("Count") +
  geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black")) 
```

### Newt and Snake Population Size
```{r, newt and snake pop size by interaction rate}
newtfig <- ggplot(GA1_lit_interrate_file)+
  ggtitle("Newt Population Size") +
  xlab("Newt_pop_size") +
  geom_histogram(aes(x = as.numeric(Newt_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      legend.position='none',
                      axis.line = element_line(colour = "black"))

snakefig <- ggplot(GA1_lit_interrate_file)+
  ggtitle("Snake Population Size") +
  xlab("Snake_pop_size") +
  geom_histogram(aes(x = as.numeric(Snake_pop_size), fill=factor(interrate)), alpha = 0.65, position="identity") +
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(),
                      legend.position='none',
                      axis.line = element_line(colour = "black"))

grid.arrange(newtfig, snakefig, ncol = 2)
```

### Newt and Snake Mean Phenotype
```{r, newt and snake meanphenotype by interaction rate}
newtfig <- ggplot(GA1_lit_interrate_file)+
  ggtitle("Newt Mean Phenotype") +
  xlab("Average Newt Phenotype") +
  geom_histogram(aes(x = as.numeric(Newt_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") + xlim(0, 12)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      legend.position='none',
                      axis.line = element_line(colour = "black"))

snakefig <- ggplot(GA1_lit_interrate_file)+
  ggtitle("Snake Mean Phenotype") +
  xlab("Average Snake Phenotype") +
  geom_histogram(aes(x = as.numeric(Snake_mean_Pheno), fill=factor(interrate)), alpha = 0.65, position="identity") + xlim(0, 12)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(),
                      legend.position='none',
                      axis.line = element_line(colour = "black"))

grid.arrange(newtfig, snakefig, ncol = 2)
```

### How Interaction rate changes the population size
```{r, tale of the interaction rate and pop size}
ggplot(GA1_lit_interrate_file)+
  ggtitle("Number of Interactions by Newt and Snake Population Size") +
  xlab("Newt Population Size") + ylab("Snake Population Size")+
  facet_wrap(~interrate)+
  geom_point(aes(x = as.numeric(Newt_pop_size), y = as.numeric(Snake_pop_size), color=newt_found), size = 1 )+
  scale_color_viridis_c(name = "newt_found")+
  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="right")
GA1_lit_interrate_file$group_rate<- paste0(GA1_lit_interrate_file$group, "_", GA1_lit_interrate_file$interrate)
last_point <- GA1_lit_interrate_file %>% group_by(group_rate) %>% slice_max(generation, with_ties = FALSE)
```

Changing the interaction rate has major consequences for my simulation. If the interaction rate is too low there is not enough selection to increase the mean phenotype of newts and snakes. If the interaction rate is too large there is too much competition between newts and snakes leading to an extinction of one of the species. In my simulation the potential interaction is noted if there is a newt near a snake. This measurement is a combination of the snakes population size and how close the species are to each other. The true number of interactions is based on a mathematical formula that increases the probably of interaction with increasing the interaction rate, but also decreases the probability of interaction with an increase in distance to a newt. This explains why low interaction rates have less interactions, while also explaining why higher interaction rates also have less interactions. Interaction rate has consequences for newt and snake population size and phenotype. At lower interaction rates newts and snakes have a higher population size, but lower mean phenotype. At slightly larger interaction rates newts and snakes have a lower population size, but a higher mean phenotype. At the largest interaction rates the newt and snake populations reach extreme population sizes and high mean phenotypes as one of the species goes extinct. For fun, I explored how each  interaction rate changed the population sizes of newts and snakes and the number of interaction that occurred. I found that an interaction rate that is too low or too high ends up having less interactions overall. There is small area of parameter space where interaction rate can be set to (0.025 to 0.075).

surs = 0.5
mPoint = c(ind_snake.x,ind_snake.y);
newtNeighbors = i1.nearestNeighborsOfPoint(p1, mPoint, count=1000000);// could make count smaller (limit the number of newts nearby)
distance = i1.distanceToPoint(newtNeighbors, mPoint);// vector of distances 
probablity = interaction_rate * exp(-(distance^2)/(2*(surs^2)))
newt_meet_snake = newtNeighbors[runif(length(newtNeighbors)) < probablity]
distance might go up and down based on how close newts and snakes

```{r, extra plots that deminstrate that it is consistance across the GA combos}
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("snake_found_newt") +
#   xlab("Generations") + ylab("snake_found_newt")+
#   geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("snake_found_newt") +
#   xlab("Generations") + ylab("snake_found_newt")+
#   facet_wrap(~group)+
#   geom_point(aes(x = as.numeric(generation), y = as.numeric(snake_found_newt), color=factor(interrate)), size = 1 )+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("newt_found") +
#   xlab("Generations") + ylab("newt_found")+
#   facet_wrap(~group)+
#   geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("newt_found") +
#   xlab("Generations") + ylab("newt_found")+
#   geom_point(aes(x = as.numeric(generation), y = as.numeric(newt_found), color=factor(interrate)), size = 1 )+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Snake can potentially find a newt") +
#   xlab("snake_found_newt") +
#   geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Snake can potentially find a newt") +
#   xlab("snake_found_newt") +
#   geom_histogram(aes(x = as.numeric(snake_found_newt), fill=factor(interrate)),  alpha = 0.65, position="identity")+
#   facet_wrap(~group)+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Snake found a Newt") +
#   xlab("newt_found") +
#   geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Snake age") +
#   xlab("Snake_age") +
#   geom_histogram(aes(x = as.numeric(Snake_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
#   xlim(0, 10)+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Newt age") +
#   xlab("Newt_age") +
#   geom_histogram(aes(x = as.numeric(Newt_age), fill=factor(interrate)), alpha = 0.65, position="identity") +
#   xlim(0, 10)+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Snake found a Newt") +
#   xlab("newt_found") +
#   geom_histogram(aes(x = as.numeric(newt_found), fill=factor(interrate)), alpha = 0.65, position="identity") +
#   facet_wrap(~group)+
#   theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
#                       # strip.background = element_blank(), 
#                       # strip.text.x = element_blank(), 
#                       # panel.grid.major = element_blank(), 
#                       # panel.grid.minor = element_blank(),
#                       # panel.background = element_blank(), 
#                       axis.line = element_line(colour = "black")) 
# 
# 
# ggplot(GA1_lit_interrate_file)+
#   ggtitle("Newt_pop_size") +
